---
title: "Developing Data Products | Predicting Heights"
author: "Sarthak Naithani"
date: "11/4/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary
This presentation is in corresponding to the Developing Data products assignment, for predictiong height of the child by taking in consideration the gender of child and height of parents.

Getting Started:
1. A shiny application is made which contains server.R and ui.R file.
2. The application takes Father's height, Mother;s height and Gender of the child as the input.
3. The output is the child's height, shown n form of a bar graph.

## DataSet used:
I have used Galton Families dataset, and have used lnear model to predict the child's height.

The application is running on the link (https://sarthakapps.shinyapps.io/PredictHeight/)

ui.R, and Server.R Code in my github repository (https://github.com/XavierFontane/Course-Project-Shiny-Application-and-Reproducible-Pitch)

```{r summary}
library(HistData)
data(GaltonFamilies)
summary(GaltonFamilies)
```

## Plot
The data used for prediction of the model is presented in the scatter plot below

```{r plot}
library(HistData)
data(GaltonFamilies)
plot(jitter(GaltonFamilies$childHeight) ~ GaltonFamilies$midparentHeight,xlab="Average Height of the Parents (in inches)",ylab="Height of the Child (in inches)",main="Scatterplot of Galton Family Data",pch=19,frame.plot=FALSE,col=ifelse(GaltonFamilies$gender=="female", "pink", "light blue"))
legend(65,80,pch=c(19,19),col=c("pink","light blue"),c("female", "male"),bty="o",cex=.8)
```

Thank You
----
